Type Refinements for the Working Class

### 2016-01-01 paper.tex
wordsmithing

  In fact, far from being a technical nuisance, the definition that is forced
  by the nature of our presuppositions is completely desirable, since it
  expresses a \emph{behavioral} notion of independence rather than a
  \emph{structural} one. Moreover, under the structural definition, even if
  $\phi$ is a type, $\phi\setminus a$ might fail to be a type in case there is
  a member of $\phi$ that uses $a$ which is merely computationally equivalent
  to another member that is independent of $a$.
\end{remark}

>>>>

  In fact, far from being a technical nuisance, the definition that is forced
  by the nature of our presuppositions is completely desirable, since it
  expresses the \emph{behavioral} notion of independence rather than the
  \emph{structural} one. Moreover, under the structural definition, even if
  $\phi$ is a type, $\phi\setminus a$ might fail to be a type in case there is
  a member of $\phi$ that uses $a$ which is merely computationally equivalent
  to another member that is independent of $a$.
\end{remark}
